### 2016-06-27 publications/Journal/1-introduction.tex
Update abstract and introduction
Signed-off-by: Ben Cardoen <bencardoen@gmail.com>

This paper introduces DEVS-Ex-Machina\footnote{\url{https://bitbucket.org/bcardoen/devs-ex-machina}} (``dxex''), our simulation tool which offers multiple synchronization protocols: no synchronization (sequential execution), conservative synchronization, or optimistic synchronization.
The selected synchronization protocol is transparent to the simulated model: users should merely determine, which protocol they wish to use.
Users who simulate a wide variety of models, with different ideal synchronization protocols, can simply run the same model with different synchronization protocols.
We investigate in this paper how model allocation and uncertainty determine the choice between synchronization protocols. The synchronization overhead is demonstrated by reducing the computational load of a model to near zero. Dxex also offers a visualization of the simulation with in depth statistics on the synchronization algorithms. With all this information the modeller can make the best informed decision on which synchronization algorithm to use.

@@

% TODO uncomment if completed
%Dxex offers online switching functionality that can be used by machine learning %techniques to automatically switch between the most optimal synchronzation protocol.

>>>>

This paper introduces DEVS-Ex-Machina\footnote{\url{https://bitbucket.org/bcardoen/devs-ex-machina}} (``dxex''), our simulation tool which offers multiple synchronization protocols: no synchronization (sequential execution), conservative synchronization, or optimistic synchronization.
The selected synchronization protocol is transparent to the simulated model: users should merely determine, which protocol they wish to use.
Users who simulate a wide variety of models, with different ideal synchronization protocols, can simply run the same model with different synchronization protocols.
We investigate in this paper how model allocation and uncertainty determine the choice between synchronization protocols. 
The synchronization overhead is demonstrated by reducing the computational load of a model to near zero.

@@

% Switching and statistics
Dxex offers visualization of the simulation and in depth statistics. A modeller can then make a more informed decision on which synchronization protocol to use or even intervene during simulation and request a switch between protocols.

### 2016-06-27 publications/Journal/abstract.tex
Slight modification of abstract.
Signed-off-by: Ben Cardoen <bencardoen@gmail.com>
Update abstract and introduction
Signed-off-by: Ben Cardoen <bencardoen@gmail.com>

With the ever increasing complexity of simulation models, parallel simulation
becomes necessary to perform the simulation within reasonable time bounds.
The built-in parallelism of Parallel DEVS is often insufficient to tackle this problem on its own.
Several synchronization protocols have been proposed, each with their distinct advantages and disadvantages.
Due to the significantly different implementation of these protocols, most Parallel DEVS simulation tools are limited to only one such protocol.
In this paper, we present a Parallel DEVS simulator, grafted on C++14, but based on PythonPDEVS, which supports both conservative and optimistic synchronization.
We evaluate the performance gain obtained by choosing the most appropriate synchronization protocol.
Performance results are compared to adevs, in terms of CPU time and memory usage.

>>>>

With the ever increasing complexity of simulation models, parallel simulation
becomes necessary to perform the simulation within reasonable time bounds.
The built-in parallelism of Parallel DEVS is often insufficient to tackle this problem on its own.
Several synchronization protocols have been proposed, each with their distinct advantages and disadvantages.
Due to the significantly different implementation of these protocols, most Parallel DEVS simulation tools are limited to only one such protocol.
In this paper, we present a Parallel DEVS simulator, grafted on C++11, but based on PythonPDEVS, which supports both conservative and optimistic synchronization protocols with the capability to switch during simulation between those protocols.
We evaluate the performance gain obtained by choosing the most appropriate synchronization protocol and demonstrate the inlfuence model allocation and uncertainty has on this choice. 
Performance results are compared to adevs, in terms of CPU time and memory usage.
